\documentclass[17pt]{extarticle}
\usepackage{titling}

\setlength{\droptitle}{-10em}


\setlength{\parindent}{0pt}
\setlength{\oddsidemargin}{-15pt}
\setlength{\textwidth}{480pt}
\setlength{\textheight}{730pt}

\author{Michał 'Mike' Puchyr}
\date{}
\title{\textbf{My hopes for next 50 years in terms of health and society}}

\begin{document}
\maketitle
\begin{center}
    First, I hope my country will be even more developed just around the level of western countries.
    I hope that the society will have understood that differences between people are not a reason to hate each other.
    Poland by next 50 years will also have reformed their education system which will be more focused on analytical thinking and creativity than on memorizing facts.
    
    My country will also have fixed the problem with healthcare system so that everyone in need will no longer have to wait for months (or years, or centuries) for specialist appointment.
    My expectancy is that the society will have comprehended that without environment protection is our main priority.
    I hope that my country will have maintained peace and will have not been involved in any war.
    In next half of 21-th century there also will have been developed a cure for cancer, diabetes and many other diseases which are currently incurable.
    This will surely have extended the average life expectancy above 100 years.
    Lastly, I hope that everything will have been done to prevent the climate change and that the world will have been saved from the global warming.

\end{center}

\end{document}